How I use R Markdown to write research papers

### 2021-01-21 text/20/markdown-papers.Rmd
Added niss.md

---
title: "How I use R Markdown to write research papers"
source: "New"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
---

>>>>

---
title: "How I use R Markdown to write research papers"
source: "New"
date: "2020-11-21"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
---
